---
title: ""
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for _Stachelek et al. (2017)_

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.839334.svg)](https://doi.org/10.5281/zenodo.839334)

**Joseph Stachelek, Christopher J. Madden, Stephen Kelly, Michelle Blaha (submitted)**. Improved estimation of phytoplankton abundance and fine-scale water quality features via simultaneous discrete and semi-continuous surveys.

## Dependencies
### R packages

```{r echo=FALSE}
knitr::kable(data.frame(packages1 = c("DataflowR", "raster", "ggplot2", 
                                     "dplyr", "ggrepel"), 
                        packages3 = c("ggsn", "maptools", "cowplot",
                                      "viridis", "sp"), 
                        packages2 = c("remake", "gdalUtils", "sf", 
                                     "fitdistrplus", "GGally"), 
                        packages4 = c("knitr", "kableExtra", "magrittr", 
                                      "gstat", "ggjoy")), 
             col.names = c("", "", "", ""))
```

## Data

**Christopher J. Madden, Joseph Stachelek, Stephen Kelly, Michelle Blaha (2017)** Florida Bay water quality estimated by underway flow-through measurement. _KNB Data Repository_. [http://dx.doi.org/10.5063/F11R6NGR](http://dx.doi.org/10.5063/F11R6NGR)

## Build

Building the figures, tables, and manuscript has been streamlined with [GNU make](http://kbroman.org/minimal_make/). See the items defined as build targets by running the following line in the terminal:

`$ make help`

```{bash echo=FALSE}
make help_no_color
```
